Analysis plan

### 2023-01-30 02. Design/MSG-P2312-Analysis Plan-2-sequence.rmd
Create MSG-P2312-Analysis Plan-2-sequence.rmd
Removed references to clusters.

---
title: "Analysis plan"
# date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Sara Guenther and Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  analysis_plan_title: "Phase 2 - Clusters"
editor_options: 
  markdown: 
    wrap: 72
---

@@

# Analysis Plan

@@

```{r}
tbl <- tibble("Variable Name" = c(
  "date",
"SSO",
"short_id",
"dept_id",
"employee_name",
"supervisor_name",
"location",
"daily_status",
"supervisor_correction"
),
"Description" = c(
  "Date of check-in",
  # Is SSO single sign on? What did we decide?
"",
"2-digit department id",
"Full department id code",
"Employee name (Last,First Middle)",
"Supervisor name (Last,First Middle)",
"State abbreviation-City-Site (e.g., home or address); could string split and match state with roster, possibly city too.",
"E.g., Teleworking, Leave, Supervisor Corrected, No Response, Reporting to Job Site, Other",
# I think that this is an indicator for whether the supervisor corrected the record
""
)
)
```

```{r}
tbl %>% 
  flextable() %>% 
  # add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
  # set_header_labels(Group = "Level of analysis") %>% 
  merge_h(part = "header") %>% 
  merge_v(j = 1) %>% 
  theme_vanilla() %>% 
  autofit()
```

@@

```{r}
tbl <- tibble("Variable Name" = c(
"Snapshot.Date",
"Department.ID",
"Employee.Job.Business.Unit.Description",
"Full.Name",
"Employee.E.Mail.Address",
"Position.Title",
"Pay.Plan",
"Occupational.Series",
"Grade",
"EOD.Date",
"Supervisor.Level",
"Supervisor.Level.Description",
"Supervisor.Display.Name",
"Supervisor.E.Mail.Address",
"Business.Line.2.Letter.Department.ID.",
"GSA.SSO",
"Agency.Subelement.Code.Description",
"GSA.Region",
"GSA.Duty.Station.Region",
"Location.City",
"Location.State",
"Duty.Station.Code",
"Employee.Job.Bargaining.Unit.Description",
"Employee.Summary.Bargaining.Unit",
"Payroll.Accounting.Code",
"Position.Number",
"Position.Category.Code",
"Position.Category.Description"
),
"Description" = c(
 "Date of data export",
"Should align with check-in’s 'dept_id'",
"",
"Last,First Middle; should align with check-in’s 'employee_name'",
"",
"",
"",
"",
"",
"",
"",
"",
"First, Last",
"",
"",
"",
"",
"",
"",
"",
"",
"",
"",
"",
"",
"",
"",
"E.g., Onsite flexible, Offsite, Onsite required, Not specified, Position has changed"
)
)
```

```{r}
tbl %>% 
  flextable() %>% 
  # add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
  # set_header_labels(Group = "Level of analysis") %>% 
  merge_h(part = "header") %>% 
  merge_v(j = 1) %>% 
  theme_vanilla() %>% 
  autofit()
```

@@

For much of this study, no particular outcome will be analyzed. For
cluster and categorization, we will use various measures of staff work
location and frequency, for example, proportion of time teleworking or
frequency of teleworking on particular days.

@@

The analysis will be done for staff and teams separately

```{r, echo=FALSE}
tbl <- 
  tibble::tibble(
    # level = rep("Level of analysis",2),
                      Group = c("Staff", "Team"),
                      Cluster = c("Person level aggregation of work status", "Team level aggregation of work status"),
                      # Sequence = c("Daily person work status", "Daily team work status")
                       )
```

@@

We will approach grouping staff and teams in two ways. First, rules-based groups will be formed. For these, definitions of different types of work will be defined. Second, groups will be formed using k-means clustering. This unsupervised machine learning method produces a defined number of groups (or clusters) minimizing the distance between the members.

<!-- https://www.r-bloggers.com/2021/04/cluster-analysis-in-r/ -->
<!-- https://www.guru99.com/r-k-means-clustering.html -->

@@

Three broad parts of descriptive work are part of this analysis. First, the overall description of work patterns in the data. Then, differences in work patterns by rules-based group, and differences in descriptive data by those groups. Lastly, difference in k-means cluster by work patterns and descriptive data.

>>>>

---
title: "Analysis plan"
# date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Sara Guenther and Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  analysis_plan_title: "Phase 2 - Sequences"
editor_options: 
  markdown: 
    wrap: 72
---

@@

@@

@@

@@

For much of this study, no particular outcome will be analyzed. For
cluster and categorization, we will use various measures of staff work
location and frequency, for example, proportion of time teleworking or
frequency of teleworking on particular days. For sequence analysis, we
will use work status on particular days for staff or in combination with
team members.

@@

The analysis can be thought of as a two-by-two box.

```{r, echo=FALSE}
tbl <- 
  tibble::tibble(
    # level = rep("Level of analysis",2),
                      Group = c("Staff", "Team"),
                      # Cluster = c("Person level aggregation of work status", "Team level aggregation of work status"),
                      Sequence = c("Daily person work status", "Daily team work status")
                       )
```

@@

@@
